Paper Figure Generation

### 2022-07-20 R/PaperFigureGeneration.rmd
Update PaperFigureGeneration.rmd
Ummm... Lots of changes here. Mainly reorganized/added supplemental figures to emphasize patterns on 5' cut site.

NHF1CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
NHF1SixFourTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
arabidopsisCPDTimepoints = list(`ZT2` = NULL, `ZT14` = NULL)
yeastCPDTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
GM12878CisplatinTimepoints = list(`90min` = NULL)
CSBCPDTimepoints = list(`1h` = NULL)
XPCCPDTimepoints = list(`1h` = NULL)

@@

GM12878DataDirectory = file.path(deaminationDataDirectory, "GM12878")
GM12878SequenceAndPositionDataDirectory = file.path(GM12878DataDirectory, "sequence_and_position_analysis")

@@

XPCDataDirectory = file.path(deaminationDataDirectory, "XP-C")
XPCSequenceAndPositionDataDirectory = file.path(XPCDataDirectory, "sequence_and_position_analysis")
```

@@

```{r read_figure_4_data}
NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered = fread(generateFilePath(
  NHF1ExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
  cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
  strandPolarity = "three_prime", anchored = TRUE, filtering = "TGG_filtered"
))

NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered = NHF1CPDTimepoints
for (i in seq_along(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)) {
  NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered[[i]] = fread(generateFilePath(
    NHF1ExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
    timepoint = names(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)[i],
    strandPolarity = "three_prime", anchored = TRUE, sequence = "YR", filtering = "TGG_filtered"
  ))
}
```

@@

### All timepoints together ###
# plotNucFreqVsReadLengthBarPlot(NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered, 
#                                title = "NHF1 CPD ALL Reps TGG-Filtered 3' Anchored Purine Freq",
#                                yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
#                                combineNucleotides = c("AG"), combinedNames = c("Purine"),
#                                posType = THREE_PRIME, showFivePrimeCutSite = TRUE,
#                                expansionOffset = 10, minReadLength = 19, maxReadLength = 25,
#                                xAxisLabel = "Mismatch Relative Position")
```
```{r figure_4B, fig.width = 5, fig.height = 5}
### Just the 1h timepoint ###
plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered$`1h`,
                        title = "NHF1 CPD 1h All Reps TGG-Filtered 3' Anchored YR Freq",
                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
                        expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 8,
                        endBasedCheckPositions = -10, displayPValue = TRUE, xAxisLabel = "Mismatch Relative Position")

@@

### All timepoints together ###
# plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsTGGFiltered, 
#                                title = "NHF1 CPD All Reps TGG-Filtered 5' Anchored Nuc Freq",
#                                secondaryYAxisLabel = "3' Cut Site Distance",
#                                posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
#                                expansionOffset = 10, minReadLength = 1, maxReadLength = 8,
#                                xAxisLabel = "Mismatch Relative Position")
```

```{r figure_S3B, fig.width = 6.5, fig.height = 6}
### Just the 1h timepoint ###
plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsTGFiltered[Timepoint == "1h"], 
                               title = "NHF1 CPD 1h All Reps TG-Filtered 5' Anchored Nuc Freq",
                               secondaryYAxisLabel = "3' Cut Site Distance",
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
                               expansionOffset = 10, minReadLength = 1, maxReadLength = 8,
                               xAxisLabel = "Mismatch Relative Position")

### All timepoints together ###
# plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsTGFiltered, 
#                                title = "NHF1 CPD All Reps TG-Filtered 5' Anchored Nuc Freq",
#                                secondaryYAxisLabel = "3' Cut Site Distance",
#                                posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
#                                expansionOffset = 10, minReadLength = 1, maxReadLength = 8,
#                                xAxisLabel = "Mismatch Relative Position")
```

```{r figure_S3D, fig.width = 5, fig.height = 5}
### Just the 1h timepoint ###
plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsTGFiltered["1h"], includedTypes = c("C>T"),
                                         title = "NHF1 CPD 1h All Reps TG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = NHF1CPDMMFreqZScoresAllRepsTGFiltered,
                                         posType = THREE_PRIME, yAxisLabel = "Relative C>T Frequency")

@@

```{r figure_S4, fig.width = 9, fig.height = 5}
plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsTGGFiltered,
                               title = "NHF1 CPD ALL Reps TGG-Filtered 5' Anchored Purine Freq",
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
                               expansionOffset = 10, minReadLength = 1, maxReadLength = 7,
                               xAxisLabel = "Mismatch Relative Position")
```

@@

yeastThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered = yeastCPDTimepoints
for (i in seq_along(yeastThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)) {
  yeastThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered[[i]] = fread(generateFilePath(
    yeastExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
    cellType = "yeast", lesion = "CPD", repitition = "all_reps",
    timepoint = names(yeastThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)[i],
    strandPolarity = "three_prime", anchored = TRUE, sequence = "YR", filtering = "TGG_filtered"
  ))
}
```

```{r figure_S5, fig.width = 9, fig.height = 5}
plotSequenceFrequencies(arabidopsisThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered,
                        title = "Arabidopsis CPD ZT2 All Reps TGG-Filtered 3' Anchored YR Freq",
                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
                        expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 8,
                        endBasedCheckPositions = 10, displayPValue = TRUE, xAxisLabel = "Mismatch Relative Position")

plotSequenceFrequencies(yeastThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered,
                        title = "Yeast CPD 20min All Reps TGG-Filtered 3' Anchored YR Freq",
                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
                        expansionOffset = 10, minReadLength = 13, maxReadLength = 19, endBasedBackgroundNum = 8,
                        endBasedCheckPositions = -10, displayPValue = TRUE, xAxisLabel = "Mismatch Relative Position")
```

>>>>

NHF1CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
NHF1SixFourTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
arabidopsisCPDTimepoints = list(`ZT2` = NULL, `ZT14` = NULL)
yeastCPDTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
GM12878CisplatinTimepoints = list(`90min` = NULL)
CSBCPDTimepoints = list(`1h` = NULL)
XPCCPDTimepoints = list(`1h` = NULL)
EColiCPDTimepoints = list(`5min` = NULL)

@@

GM12878DataDirectory = file.path(deaminationDataDirectory, "GM12878")
GM12878SequenceAndPositionDataDirectory = file.path(GM12878DataDirectory, "sequence_and_position_analysis")
GM12878GeneralReadSequenceDataDirectory = file.path(GM12878DataDirectory, "general_read_sequences")

@@

XPCDataDirectory = file.path(deaminationDataDirectory, "XP-C")
XPCSequenceAndPositionDataDirectory = file.path(XPCDataDirectory, "sequence_and_position_analysis")

EColiDataDirectory = file.path(deaminationDataDirectory, "E_coli_WT")
EColiExcisionSiteDataDirectory = file.path(EColiDataDirectory, "excision_site_analysis")
```

@@

```{r read_figure_4_data}
NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered = fread(generateFilePath(
  NHF1ExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
  cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
  strandPolarity = "three_prime", anchored = TRUE, filtering = "TGG_filtered"
))
NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered = NHF1CPDTimepoints
for (i in seq_along(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)) {
  NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered[[i]] = fread(generateFilePath(
    NHF1ExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
    timepoint = names(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)[i],
    strandPolarity = "three_prime", anchored = TRUE, sequence = "YR", filtering = "TGG_filtered"
  ))
}
```

@@

### All timepoints together ###
# plotNucFreqVsReadLengthBarPlot(NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered, 
#                                title = "NHF1 CPD ALL Reps TGG-Filtered 3' Anchored Purine Freq",
#                                yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
#                                combineNucleotides = c("AG"), combinedNames = c("Purine"),
#                                posType = THREE_PRIME, showFivePrimeCutSite = TRUE,
#                                expansionOffset = 10, minReadLength = 19, maxReadLength = 25,
#                                xAxisLabel = "Mismatch Relative Position")
```
```{r figure_4B, fig.width = 5, fig.height = 5}
# ### Just the 1h timepoint (asterisks) ###
# plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered$`1h`,
#                         title = "NHF1 CPD 1h All Reps TGG-Filtered 3' Anchored YR Freq",
#                         secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
#                         showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
#                         expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 8,
#                         endBasedCheckPositions = -10, xAxisLabel = "Mismatch Relative Position",
#                         significanceAsteriskBreakpoints = c(1e-6, 1e-9))

## Just the 1h timepoint (full p-values) ###
plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered$`1h`,
                        title = "NHF1 CPD 1h All Reps TGG-Filtered 3' Anchored YR Freq",
                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
                        expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 8,
                        endBasedCheckPositions = -10, displayPValue = TRUE, xAxisLabel = "Mismatch Relative Position")

@@

### All timepoints together ###
# plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsTGGFiltered, 
#                                title = "NHF1 CPD All Reps TGG-Filtered 5' Anchored Nuc Freq",
#                                secondaryYAxisLabel = "3' Cut Site Distance",
#                                posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
#                                expansionOffset = 10, minReadLength = 1, maxReadLength = 8,
#                                xAxisLabel = "Mismatch Relative Position")
```
```{r figure_S3B, fig.width = 6.5, fig.height = 6}
### Just the 1h timepoint ###
plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsTGFiltered[Timepoint == "1h"], 
                               title = "NHF1 CPD 1h All Reps TG-Filtered 5' Anchored Nuc Freq",
                               secondaryYAxisLabel = "3' Cut Site Distance",
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
                               expansionOffset = 10, minReadLength = 1, maxReadLength = 8,
                               xAxisLabel = "Mismatch Relative Position")

### All timepoints together ###
# plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsTGFiltered, 
#                                title = "NHF1 CPD All Reps TG-Filtered 5' Anchored Nuc Freq",
#                                secondaryYAxisLabel = "3' Cut Site Distance",
#                                posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
#                                expansionOffset = 10, minReadLength = 1, maxReadLength = 8,
#                                xAxisLabel = "Mismatch Relative Position")
```
```{r figure_S3D, fig.width = 5, fig.height = 5}
### Just the 1h timepoint ###
plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsTGFiltered["1h"], includedTypes = c("C>T"),
                                         title = "NHF1 CPD 1h All Reps TG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = NHF1CPDMMFreqZScoresAllRepsTGFiltered,
                                         posType = THREE_PRIME, yAxisLabel = "Relative C>T Frequency")

@@

```{r read_figure_S4_data}
EColiThreePrimeMismatchCPDNucFreqAllReps = fread(generateFilePath(
  EColiExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
  cellType = "E_coli_WT", lesion = "CPD", repitition = "all_reps",
  strandPolarity = "three_prime", anchored = TRUE
))
EColiThreePrimeMMAnchoredCPDSeqFreqAllReps = EColiCPDTimepoints
for (i in seq_along(EColiThreePrimeMMAnchoredCPDSeqFreqAllReps)) {
  EColiThreePrimeMMAnchoredCPDSeqFreqAllReps[[i]] = fread(generateFilePath(
    EColiExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
    cellType = "E_coli_WT", lesion = "CPD", repitition = "all_reps",
    timepoint = names(EColiThreePrimeMMAnchoredCPDSeqFreqAllReps)[i],
    strandPolarity = "three_prime", anchored = TRUE, sequence = "YR"
  ))
}
```

```{r figure_S4A, fig.width = 6.5, fig.height = 6}
plotNucFreqVsReadLengthBarPlot(NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered[Timepoint == "1h"], 
                               title = "NHF1 CPD 1h All Reps TGG-Filtered 3' Anchored Nuc Freq",
                               secondaryYAxisLabel = "5' Cut Site Distance",
                               posType = FIVE_PRIME, showFivePrimeCutSite = TRUE,
                               expansionOffset = 10, minReadLength = 19, maxReadLength = 25,
                               xAxisLabel = "Mismatch Relative Position")
```
```{r figure_S4B, fig.width = 5, fig.height = 6}
plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsTGFiltered[Timepoint == "1h"],
                               title = "NHF1 CPD 1h ALL Reps TG-Filtered 5' Anchored Purine Freq",
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
                               expansionOffset = 10, minReadLength = 6, maxReadLength = 13,
                               xAxisLabel = "Mismatch Relative Position")
```
```{r figure_S4C}
plotNucFreqVsReadLengthBarPlot(EColiThreePrimeMismatchCPDNucFreqAllReps,
                               title = "NHF1 E coli ALL Reps 5' Anchored Purine Freq",
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = FIVE_PRIME, showFivePrimeCutSite = TRUE,
                               expansionOffset = 10,
                               xAxisLabel = "Mismatch Relative Position")
```
```{r figure_S4D}
plotSequenceFrequencies(EColiThreePrimeMMAnchoredCPDSeqFreqAllReps,
                        title = "E coli CPD 30min All Reps 3' Anchored YR Freq",
                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
                        expansionOffset = 10, xAxisLabel = "Mismatch Relative Position")
```

@@

yeastThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered = yeastCPDTimepoints
for (i in seq_along(yeastThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)) {
  yeastThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered[[i]] = fread(generateFilePath(
    yeastExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
    cellType = "yeast", lesion = "CPD", repitition = "all_reps",
    timepoint = names(yeastThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)[i],
    strandPolarity = "three_prime", anchored = TRUE, sequence = "YR", filtering = "TGG_filtered"
  ))
}

NHF1SixFour20MinSeqFreqAllRepsFiltered = fread(generateFilePath(
  NHF1GeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
  cellType = "NHF1", lesion = "6-4", timepoint = "20min",
  repitition = "all_reps", sequence = "YR", filtering = "TGG_filtered"
))
NHF1SixFour20MinSeqFreqAllRepsFiltered[, Position := Position + 10]
endPositionsByTimepointAndRL = NHF1SixFour20MinSeqFreqAllRepsFiltered[, .(End = max(abs(Position))),
                                                      by = Read_Length]
setkey(endPositionsByTimepointAndRL, Read_Length)
endPosByFullFreqRow = endPositionsByTimepointAndRL[list(NHF1SixFour20MinSeqFreqAllRepsFiltered$Read_Length)]$End
seqFreqPlottingRows = NHF1SixFour20MinSeqFreqAllRepsFiltered[abs(Position) + abs(17) > endPosByFullFreqRow]

GM12878Cisplatin90MinSeqFreqRep1Filtered = fread(generateFilePath(
  GM12878GeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
  cellType = "GM12878", lesion = "cisplatin", timepoint = "90min",
  repitition = "rep1", sequence = "YR", filtering = "TGG_filtered"
))
GM12878Cisplatin90MinSeqFreqRep1Filtered[, Position := Position + 10]
endPositionsByTimepointAndRL = GM12878Cisplatin90MinSeqFreqRep1Filtered[, .(End = max(abs(Position))),
                                                      by = Read_Length]
setkey(endPositionsByTimepointAndRL, Read_Length)
endPosByFullFreqRow = endPositionsByTimepointAndRL[list(GM12878Cisplatin90MinSeqFreqRep1Filtered$Read_Length)]$End
seqFreqPlottingRows = GM12878Cisplatin90MinSeqFreqRep1Filtered[abs(Position) + abs(17) > endPosByFullFreqRow]
```

```{r figure_S5, fig.width = 5, fig.height = 6}
plotSequenceFrequencies(arabidopsisThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered$ZT2,
                        title = "Arabidopsis CPD All Reps TGG-Filtered 3' Anchored YR Freq",
                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
                        expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 8,
                        endBasedCheckPositions = 10, displayPValue = TRUE, xAxisLabel = "Mismatch Relative Position")

plotSequenceFrequencies(yeastThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered$`20min`,
                        title = "Yeast CPD All Reps TGG-Filtered 3' Anchored YR Freq",
                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
                        expansionOffset = 10, minReadLength = 13, maxReadLength = 19, endBasedBackgroundNum = 8,
                        endBasedCheckPositions = -10, displayPValue = TRUE, xAxisLabel = "Mismatch Relative Position")

plotSequenceFrequencies(NHF1SixFour20MinSeqFreqAllRepsFiltered,
                        title = "NHF1 6-4 All Reps TGG-Filtered YR Freq",
                        secondaryYAxisLabel = "Read Length", yAxisLabel = "YR Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"), expansionOffset = 10,
                        minReadLength = 22, maxReadLength = 30, endBasedBackgroundNum = 8,
                        endBasedCheckPositions = -10, displayPValue = TRUE, xAxisLabel = "3' Relative Position")

plotSequenceFrequencies(GM12878Cisplatin90MinSeqFreqRep1Filtered,
                        title = "GM12878 Cisplatin All Reps TGG-Filtered YR Freq",
                        secondaryYAxisLabel = "Read Length", yAxisLabel = "YR Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"), expansionOffset = 10,
                        minReadLength = 22, maxReadLength = 30, endBasedBackgroundNum = 8,
                        endBasedCheckPositions = -10, displayPValue = TRUE, xAxisLabel = "3' Relative Position")
```
